### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/Decile/030_employement_industry_thresh.tex
back up before new paper

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:19:11
\begin{table}[!htbp] \centering 
  \caption{Cumulative Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.409 & $-$0.803$^{***}$ & $-$0.563 & $-$0.544$^{**}$ & $-$0.332$^{*}$ & $-$0.317$^{**}$ & $-$0.272$^{**}$ & $-$0.248$^{*}$ & $-$0.136 \\ 
  & (0.569) & (0.263) & (0.350) & (0.245) & (0.173) & (0.150) & (0.131) & (0.130) & (0.127) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 1,503 & 3,880 & 6,075 & 9,103 & 13,531 & 17,657 & 21,287 & 23,930 & 27,698 \\ 
R$^{2}$ & 0.925 & 0.889 & 0.871 & 0.855 & 0.858 & 0.852 & 0.856 & 0.855 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

>>>>

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:25:09
\begin{table}[!htbp] \centering 
  \caption{Deciles Employment} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.750$^{**}$ & 0.079 & $-$1.013$^{***}$ & 2.539$^{*}$ & 0.337 & $-$0.403 & 0.436$^{**}$ & 0.472 & 0.316 \\ 
  & (0.304) & (0.732) & (0.348) & (1.523) & (0.584) & (0.305) & (0.205) & (0.716) & (0.373) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 1,582 & 1,864 & 2,842 & 1,995 & 3,603 & 5,357 & 5,229 & 2,261 & 3,881 \\ 
R$^{2}$ & 0.922 & 0.910 & 0.907 & 0.892 & 0.868 & 0.885 & 0.896 & 0.916 & 0.882 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/Decile/031_employement_industry_thresh.tex
back up before new paper

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:25:09
\begin{table}[!htbp] \centering 
  \caption{Deciles Employment} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.750$^{**}$ & 0.079 & $-$1.013$^{***}$ & 2.539$^{*}$ & 0.337 & $-$0.403 & 0.436$^{**}$ & 0.472 & 0.316 \\ 
  & (0.304) & (0.732) & (0.348) & (1.523) & (0.584) & (0.305) & (0.205) & (0.716) & (0.373) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 1,582 & 1,864 & 2,842 & 1,995 & 3,603 & 5,357 & 5,229 & 2,261 & 3,881 \\ 
R$^{2}$ & 0.922 & 0.910 & 0.907 & 0.892 & 0.868 & 0.885 & 0.896 & 0.916 & 0.882 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

>>>>

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:25:31
\begin{table}[!htbp] \centering 
  \caption{Cumulative Deciles employment} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.750$^{**}$ & $-$0.604 & $-$0.541$^{*}$ & $-$0.492 & $-$0.254 & $-$0.385$^{***}$ & $-$0.204 & $-$0.185 & $-$0.136 \\ 
  & (0.304) & (0.470) & (0.299) & (0.316) & (0.251) & (0.149) & (0.140) & (0.129) & (0.121) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 1,582 & 3,446 & 6,288 & 8,283 & 11,886 & 17,243 & 22,472 & 24,733 & 28,614 \\ 
R$^{2}$ & 0.922 & 0.889 & 0.875 & 0.861 & 0.847 & 0.851 & 0.854 & 0.852 & 0.848 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/Decile/040_output_city_thresh.tex
back up before new paper

\begin{document}% Date and time: Sun, Mar 29, 2020 - 10:34:53
\begin{table}[!htbp] \centering 
  \caption{Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.226 & $-$0.353 & $-$1.304$^{***}$ & $-$0.582 & $-$0.237 & $-$0.010 & $-$0.018 & 0.331 & 0.316 \\ 
  & (0.562) & (0.471) & (0.422) & (0.607) & (0.474) & (0.266) & (0.343) & (0.319) & (0.407) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 929 & 1,898 & 2,922 & 2,263 & 3,718 & 3,705 & 5,574 & 3,458 & 3,874 \\ 
R$^{2}$ & 0.966 & 0.893 & 0.900 & 0.895 & 0.877 & 0.905 & 0.881 & 0.896 & 0.889 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

>>>>

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:36:11
\begin{table}[!htbp] \centering 
  \caption{Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.985$^{*}$ & 0.072 & $-$0.004 & $-$0.115 & 0.063 & $-$0.358 & $-$0.696$^{*}$ & $-$0.306 & $-$0.017 \\ 
  & (0.545) & (0.360) & (0.349) & (0.536) & (0.570) & (0.444) & (0.383) & (0.601) & (0.461) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 3,343 & 3,747 & 3,930 & 3,591 & 2,909 & 2,813 & 2,878 & 2,374 & 3,493 \\ 
R$^{2}$ & 0.905 & 0.884 & 0.895 & 0.891 & 0.919 & 0.921 & 0.897 & 0.902 & 0.901 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/Decile/041_output_city_cum.tex
back up before new paper

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:19:11
\begin{table}[!htbp] \centering 
  \caption{Cumulative Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.409 & $-$0.803$^{***}$ & $-$0.563 & $-$0.544$^{**}$ & $-$0.332$^{*}$ & $-$0.317$^{**}$ & $-$0.272$^{**}$ & $-$0.248$^{*}$ & $-$0.136 \\ 
  & (0.569) & (0.263) & (0.350) & (0.245) & (0.173) & (0.150) & (0.131) & (0.130) & (0.127) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 1,503 & 3,880 & 6,075 & 9,103 & 13,531 & 17,657 & 21,287 & 23,930 & 27,698 \\ 
R$^{2}$ & 0.925 & 0.889 & 0.871 & 0.855 & 0.858 & 0.852 & 0.856 & 0.855 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

>>>>

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:38:46
\begin{table}[!htbp] \centering 
  \caption{Cumulative Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.985$^{*}$ & $-$0.190 & $-$0.042 & $-$0.099 & $-$0.035 & $-$0.121 & $-$0.161 & $-$0.158 & $-$0.150 \\ 
  & (0.545) & (0.237) & (0.177) & (0.165) & (0.164) & (0.148) & (0.136) & (0.131) & (0.124) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 3,343 & 7,090 & 11,020 & 14,611 & 17,520 & 20,333 & 23,211 & 25,585 & 29,078 \\ 
R$^{2}$ & 0.905 & 0.874 & 0.865 & 0.857 & 0.856 & 0.856 & 0.854 & 0.853 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/Decile/050_capital_city_thresh.tex
back up before new paper

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:17:52
\begin{table}[!htbp] \centering 
  \caption{Deciles capital} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.409 & $-$0.894$^{**}$ & 1.151 & $-$0.768$^{*}$ & $-$0.134 & $-$0.560 & 0.121 & $-$0.076 & 0.910$^{***}$ \\ 
  & (0.569) & (0.349) & (0.820) & (0.437) & (0.388) & (0.436) & (0.274) & (0.611) & (0.337) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 1,503 & 2,377 & 2,195 & 3,028 & 4,428 & 4,126 & 3,630 & 2,643 & 3,768 \\ 
R$^{2}$ & 0.925 & 0.901 & 0.903 & 0.884 & 0.896 & 0.885 & 0.920 & 0.908 & 0.888 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

>>>>

\begin{document}% Date and time: Sun, Mar 29, 2020 - 12:18:31
\begin{table}[!htbp] \centering 
  \caption{Deciles capital} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.879 & $-$0.144 & $-$0.303 & 0.063 & 0.027 & $-$0.224 & $-$0.789$^{*}$ & $-$0.055 & $-$0.520 \\ 
  & (1.383) & (0.342) & (0.508) & (0.415) & (0.487) & (0.611) & (0.406) & (0.468) & (0.506) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 3,669 & 4,550 & 2,513 & 3,676 & 3,439 & 1,955 & 3,387 & 2,873 & 2,465 \\ 
R$^{2}$ & 0.900 & 0.875 & 0.923 & 0.897 & 0.895 & 0.913 & 0.908 & 0.911 & 0.904 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/Decile/051_capital_city_cum.tex
back up before new paper

\begin{document}% Date and time: Sun, Mar 29, 2020 - 12:18:31
\begin{table}[!htbp] \centering 
  \caption{Deciles capital} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.879 & $-$0.144 & $-$0.303 & 0.063 & 0.027 & $-$0.224 & $-$0.789$^{*}$ & $-$0.055 & $-$0.520 \\ 
  & (1.383) & (0.342) & (0.508) & (0.415) & (0.487) & (0.611) & (0.406) & (0.468) & (0.506) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 3,669 & 4,550 & 2,513 & 3,676 & 3,439 & 1,955 & 3,387 & 2,873 & 2,465 \\ 
R$^{2}$ & 0.900 & 0.875 & 0.923 & 0.897 & 0.895 & 0.913 & 0.908 & 0.911 & 0.904 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

>>>>

\begin{document}% Date and time: Sun, Mar 29, 2020 - 12:20:43
\begin{table}[!htbp] \centering 
  \caption{Cumulative Deciles capital} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.879 & $-$0.249 & $-$0.292 & $-$0.139 & $-$0.096 & $-$0.108 & $-$0.177 & $-$0.141 & $-$0.146 \\ 
  & (1.383) & (0.243) & (0.199) & (0.176) & (0.172) & (0.155) & (0.135) & (0.129) & (0.126) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 3,669 & 8,219 & 10,732 & 14,408 & 17,847 & 19,802 & 23,189 & 26,062 & 28,527 \\ 
R$^{2}$ & 0.900 & 0.865 & 0.866 & 0.861 & 0.855 & 0.855 & 0.854 & 0.854 & 0.852 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}
